### 2019-02-06 Sections/economics_of_the_quantum_internet.tex
Scotty fig update

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_1}
\captionspacefig \caption{Utility space for two players with access to classical computing. The bold dashed lines show the minimum utility payoff for $X$ and $Y$.\comment{Vector PDF version please}}\label{fig:game_theory_1}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_2}
\captionspacefig \caption{Utility payoff between two players in the classical computing environment. $A$ indicates the utility combination where $X$ builds the system and licenses out time to $Y$, and $B$ represents the reverse. $C$ is the point where both $X$ and $Y$ cooperate through distributed cloud computing, maximising the overall utility for both players. $A$ and $B$ derive identical utility values from the strategies, yielding symmetry about the diagonal axis. The lines $AC$ and $BC$ indicate possible solutions where mixed strategies \index{Mixed strategies} are employed, combining components of \textsc{License} and \textsc{Unify}. $C$ is also the Nash equilibrium\index{Nash equilibrium}, where cooperative bargaining would result in the best outcome overall.\comment{Vector PDF version please.}}\label{fig:game_theory_2}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_4}
\captionspacefig \caption{Utility payoff for two players with quantum computers, employing mixed strategies. $X'$ and $X''$ denote two unique solutions for $Y$ having a utility of 4. From $Y$'s perspective it makes no difference which strategy is chosen. However, $X$ can locally optimise their utility by choosing $X''$ over $X'$.\comment{Vector PDF version please.}}\label{fig:game_theory_4}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_5}
\captionspacefig \caption{Adaptive strategy revision by $X$ and $Y$, yielding incremental local utility improvements without affecting the other, progressively marches us towards the optimal point $Q$ asymptotically.\comment{Vector PDF version please.}}\label{fig:game_theory_5}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_6}
\captionspacefig \caption{Utility payoff for two players with quantum computers, employing a \textsc{Unify} strategy, under the imposition of taxation.\comment{Vector PDF version please.}}\label{fig:game_theory_6}
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_1}
\captionspacefig \caption{Utility space for two players with access to classical computing. The bold dashed lines show the minimum utility payoff for $X$ and $Y$.}\label{fig:game_theory_1}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_2}
\captionspacefig \caption{Utility payoff between two players in the classical computing environment. $A$ indicates the utility combination where $X$ builds the system and licenses out time to $Y$, and $B$ represents the reverse. $C$ is the point where both $X$ and $Y$ cooperate through distributed cloud computing, maximising the overall utility for both players. $A$ and $B$ derive identical utility values from the strategies, yielding symmetry about the diagonal axis. The lines $AC$ and $BC$ indicate possible solutions where mixed strategies \index{Mixed strategies} are employed, combining components of \textsc{License} and \textsc{Unify}. $C$ is also the Nash equilibrium\index{Nash equilibrium}, where cooperative bargaining would result in the best outcome overall.}\label{fig:game_theory_2}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_4}
\captionspacefig \caption{Utility payoff for two players with quantum computers, employing mixed strategies. $X'$ and $X''$ denote two unique solutions for $Y$ having a utility of 4. From $Y$'s perspective it makes no difference which strategy is chosen. However, $X$ can locally optimise their utility by choosing $X''$ over $X'$.}\label{fig:game_theory_4}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_5}
\captionspacefig \caption{Adaptive strategy revision by $X$ and $Y$, yielding incremental local utility improvements without affecting the other, progressively marches us towards the optimal point $Q$ asymptotically.}\label{fig:game_theory_5}
\end{figure}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.475\textwidth]{game_theory_6}
\captionspacefig \caption{Utility payoff for two players with quantum computers, employing a \textsc{Unify} strategy, under the imposition of taxation.}\label{fig:game_theory_6}
\end{figure}
